Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

```{r places_per_decade, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
              group_by(catalog, publication_decade) %>%
	      summarise(n = length(unique(na.omit(publication_place))))
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Places (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(shape = guide_legend(title = "Catalog")) +
       guides(linetype = guide_legend(title = "Catalog")) +       
       ggtitle("Unique publication places")
print(p)
```

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=5, fig.show="hold", out.width="400px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"

>>>>

```{r places_per_decade, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
              group_by(catalog, publication_decade) %>%
	      summarise(n = length(unique(na.omit(publication_place))))
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Places (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(shape = guide_legend(title = "Catalog", reverse = TRUE)) +
       guides(linetype = guide_legend(title = "Catalog", reverse = TRUE)) +       
       ggtitle("Unique publication places")
print(p)
```

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=7, fig.height=4, fig.show="hold", out.width="400px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
